\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage{lipsum}
\usepackage[margin=0.75in]{geometry}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\newenvironment{QandA}{\begin{enumerate}[label=\bfseries\arabic*.]\bfseries}
{\end{enumerate}}
\newenvironment{answered}{\par\normalfont\color{Sepia}}{}
\pagestyle{empty}

\title{Machine Learning Final Exam Study Guide}
\date{2020-04-24}

\begin{document}
\noindent%
  
\section*{Guaranteed questions}
\begin{QandA}

\item What is machine learning (ML)? 
\begin{answered} 
    A set of methods that can automatically detect patterns in
    data, and then use the uncovered patterns to predict future
    data, or to perform other kinds of decision making under
    uncertainty (such as planning how to collect more data!)
\end{answered}

\item What are the main ML types? 
\begin{answered} 
    The main types are:
    \begin{enumerate}
        \item Supervised Learning 
        \item Unsupervised Learning
        \item Semi-Supervised Learning
        \item Reinforcement Learning 
    \end{enumerate}
\end{answered}

\item What ML algorithms you studied after the midterm exam?
\begin{answered} 
    \begin{enumerate}
    \item K-Means Clustering
    \item Hierarchical Clustering
    \item Recommender Systems
    \item Large Scale and Online Learning
    \item Ensemble Learning
    \item k-Nearest Neighbors (kNNs)
    \item Principle Components Analysis (PCA)
    \item Recurrent Neural Networks
    \item Reinforcement Learning
    \item Autoencoders
    \item Bayesian Networks
    \end{enumerate}
\end{answered}

\item Which is more important to you \textemdash{} model accuracy, or model
performance, support your answer with an example? \textcolor{red}{This is a
partial answer, you need to provide a simple example and your
opinion.}

\begin{answered} 
    The model accuracy, or model performance is based on your
    opinion supported by a simple example (hint: all answers are
    correct such as either one or both together based on the
    example you provide).
\end{answered}

\item What are advantages and disadvantages of Hidden Markov Mode
\begin{answered}
    \textcolor{red}{(25 Bayesian Networks \textemdash{} Thu, Apr16}
\end{answered}
\end{QandA}

\section*{L15 K-Means Clustering \textemdash{} Tue Mar3}
\begin{QandA}
    \item List, then define the common clustering algorithms.
    \item What are the two main steps of K-means Algorithm? 
    \item Write the pseudocode of K-means Algorithm
    \item How k-means algorithm works?
    \item List advantages and disadvantages of k-Means.
\end{QandA}

\section*{L16 Hierarchical Clustering \textemdash{} Thu Mar 5}
\begin{QandA}
    \item What is cluster analysis? 
    \item What are the typical applications of cluster analysis? 
    \item List, then define the two approaches of hierarchical clustering.
    \item List all steps of the hierarchical clustering of agglomerative (bottom-up) approach.
    \item Define the dendrograms, then illustrate how do dendrograms work with a diagram.
    \item List, then define all possible methods of merging the clusters that depend on the distance measures.
    \item What are the advantages and disadvantages of hierarchical clustering?
\end{QandA}

\section*{L17 Recommender Systems \textemdash{} Tue Mar 10}
\begin{QandA}
    \item Define the recommendation systems, why using Recommender Systems?
    
    \item What types of recommendation systems, list them, then draw diagrams show the working mechanism of each?
    
    \item List advantages and disadvantages of both collaborative filtering and content-based recommenders.
    
    \item How to fill rates of users who have not rated any movies?
\end{QandA}

\section*{L18 Large Scale and Online Learning  \textemdash{}Thu Mar 12}
\begin{QandA}
    \item Supervised Learning, Semi-Supervised, and Unsupervised Learning for what kinds of applications can be used? 
          What is the different between them in terms of input and output samples?
    
    \item What are the differences between Gradient Descent types: Batch, Stochastic, and Mini batch? 
          Which one is the faster to converge? 
    
    \item What are the hardware-based solutions can be used to machine learning for big data? 
    
    \item What are the platforms for online machine learning algorithms?

\end{QandA}

\section*{L19 Ensemble Learning \textemdash{} Thu Mar 19}
\begin{QandA}
    \item Define the ensemble learning, illustrate the key motivation of the ensemble learning, then draw the general idea diagram of the ensemble learning
    
    \item List the ensemble methods that minimize variance and bias.
    
    \item What are the different methods for changing training data? List them, then illustrate the working mechanism of each method, support your working mechanisms with illustration diagrams.
    
    \item Can a set of weak learners create a single strong learner?
    
    \item What are the main features of the Random Forest method?

\end{QandA}

\section*{L20 k-Nearest Neighbors (kNNs) \textemdash{} Tue Mar 24}
\begin{QandA} 

    \item What are the Idea, algorithm, and types of the Instance-Based Learning?

    \item List the k-Nearest Neighbors (k-NNs) Main Steps.

    \item What are the three require things to implement the k-NNs?

    \item How to classify an unknown instance (sample) using the k-NNs?

    \item What are the two common distance metrics used for k-NNs?

    \item List Advantages and Disadvantages of k-NNs.

\end{QandA}

\section*{L21 Principle Components Analysis (PCA) \textemdash{} Thu Mar 26}
\begin{QandA}
    \item Define the principle components analysis (PCA), then list the 3 main fields could be used to and 3 application examples.
    \item What do we mean by the variance and covariance? List the differences between the variance and covariance.
    \item Illustrate the main tasks of the PCA Process \textemdash{} step 1.
    \item How we could derive new datasets through the PCA Process \textemdash{} step 5?
\end{QandA}

\section*{L22 Recurrent Neural Networks \textemdash{} Tue Apr 7}
\begin{QandA}
    \item Define RNNs, the show whether RNNs are Supervised or Unsupervised Learning? 
    \item What is the major difference between RNNs and FNNs? illustrate that.
    \item List types AND architectures of RNNs, then draw the architecture of traditional RNNs.
    \item List, then illustrate the three main training approaches of RNNs.
    \item What are the pros and cons of the typical RNNs architecture?
\end{QandA}

\section*{L23 Reinforcement Learning \textemdash{} Thu Apr 9}
\begin{QandA}
    \item List the four main machine learning types. 
    \item Define the reinforcement learning with a diagram, then compare between the 
          reinforcement learning and supervised learning.
    \item Draw the generic learning model to learn from data. Then define the main operations of 
          it through indicating each operation (i.e. Sensor Data, Feature Extraction, etc.) and 
          related steps.
    \item What are the key features and elements of the reinforcement learning?
    \item List the 3 types of reinforcement learning.
    \item What makes reinforcement learning different from other machine learning paradigms?
\end{QandA}

\section*{L24 Autoencoders \textemdash{} Tue Apr 14}
\begin{QandA}
    \item What are autoencoders? List the general types of autoencoders based on size of hidden layer?
    \item What are the main differences between PCA and autoencoders?
    \item List the key elements AND components of autoencoders? Then illustrate the components.
    \item List, then explain the 3 main properties AND 4 hyperparameters of autoencoders.
    \item List the 8 types AND 5 applications of autoencoders.
\end{QandA}

\section*{L25 Bayesian Networks \textemdash{} Thu Apr 16}
\begin{QandA}
    \item What are Bayesian networks (BNs)? List BN components and importance.
    \item List types of probabilistic relationships, then provide 7 real-world Bayesian network applications.
    \item Define hidden Markov model (HMM), then list and illustrate components of HMM.
    \item List, with illustration, the 4 main inference algorithms of Hidden Markov Model.
    \item What are advantages and disadvantages of Hidden Markov Model?
\end{QandA}

\end{document}
